---
title: "ST117 FINAL Written Report - Phase 2 Task B"
author: "Report Pod 041"
date: "Today's date in the format 2025-05-01" 
geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
output:
  pdf_document: default
html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

# Contributions

This submission was created by: 

1. WARWICK ID 5600761 Alex Bannister:

2. WARWICK ID 5604173 Pratham Bhargava: Phase 1: q5, q7, q8, q9

3. WARWICK ID 5627113 Yanbo Dong: Phase 2: task C

4. WARWICK ID 5645242 Daniel Guo: Phase 2: task B, Phase 1: q6

5. WARWICK ID 5650102 Jules Reinaud: Phase 2: task A


```{r setup, include=FALSE}
#Code to setup packages should go here, for example
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
```

# Setting up data frames before for phase 2 part B

```{r}
#Import the dataframes from phase 1
df_stream_wide <- readRDS("/Users/danielguo/Desktop/University/Year 1/ST117/5645242_041_WR/df_stream_wide.rds")
df_precipitation_wide <- readRDS("/Users/danielguo/Desktop/University/Year 1/ST117/5645242_041_WR/df_precipitation_wide.rds")
df_soil_wide <- readRDS("/Users/danielguo/Desktop/University/Year 1/ST117/5645242_041_WR/df_soil_wide.rds")

#Averaging the repeated sampling by the variable LCODE
df_stream_avg <- df_stream_wide %>%
  group_by(SDATE, SITECODE, LCODE) %>%
  summarise(across(where(is.numeric), \(x) mean(x, na.rm = TRUE)), .groups = "drop")

#weighted averaging considering the sampling volume (VOLUME) by the variable RID
df_soil_avg <- df_soil_wide %>%
  group_by(SDATE, SITECODE, RID) %>%
  summarise(across(where(is.numeric), \(x) weighted.mean(x, w = VOLUME, na.rm = TRUE)), .groups = "drop")

#STAGE, VACUUM, and VOLUME are only contained in some of the datasets and may be dropped unless needed.
df_stream_B <- df_stream_avg %>% 
  select(-STAGE)
df_precipitation_B <- df_precipitation_wide %>% 
  select(-VOLUME)
df_soil_B <- df_soil_avg %>% 
  select(-VACUUM, -VOLUME)
```

# Question 1 and 2

```{r}
# Function to convert the dataframes into averaged data by weeks for each sites
convert_to_weekly <- function(df, date_col = "SDATE", site_col = "SITECODE") {
  df <- df %>%
    mutate(
      DATE = as.Date(.data[[date_col]]),  #Convert date column to Date type
      YEAR = format(DATE, "%Y"), # Extract year
      WEEK = format(DATE, "%W") # Extract week
    ) %>%
    group_by(.data[[site_col]], YEAR, WEEK) %>% # Group by different site, year, and week
    summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)), .groups = "drop")  #Average numeric columns by weeks
  
  return(df)
}

# function to merge three datasets (stream, precipitation, soil)
merge_datasets <- function(stream, precipitation, soil) {
  # Rename columns to Varieble_dataset abreviations
  stream <- stream %>% rename_with(~ paste0(., "_str"), -c(SITECODE, YEAR, WEEK))
  precipitation <- precipitation %>% rename_with(~ paste0(., "_prec"), -c(SITECODE, YEAR, WEEK))
  soil <- soil %>% rename_with(~ paste0(., "_soil"), -c(SITECODE, YEAR, WEEK))
# merge and full_join all the datasets
  merged <- full_join(stream, precipitation, by = c("SITECODE", "YEAR", "WEEK")) %>%
    full_join(soil, by = c("SITECODE", "YEAR", "WEEK"))
  
  return(merged)
}

# Function to remove outliers from the applicable numeric columns using interquartile range formula
remove_outliers <- function(df) {
  df %>% mutate(across(where(is.numeric), ~ {
    Q1 <- quantile(.x, 0.25, na.rm = TRUE)
    Q3 <- quantile(.x, 0.75, na.rm = TRUE)
    IQR <- Q3 - Q1
    low <- Q1 - 1.5 * IQR
    high <- Q3 + 1.5 * IQR
    ifelse(.x < low | .x > high, NA, .x)
  }))
}

# function to compute correlation matrix of one chemical between different datasets for given site and year range and method of correlation (default for pearson)
variable_correlation <- function(merged_df, variable, site, year_range, method = "pearson") { #setting pearson as the default method
  df <- merged_df %>%
    filter(SITECODE == site, as.numeric(YEAR) %in% year_range) %>%
    select(matches(paste0("^", variable, "_"))) %>%
    na.omit()
  
  if (nrow(df) < 2) {
    stop("Not enough data for correlation.")  #hault if insufficient data
  }

  if (sum(complete.cases(df)) / nrow(df) < 0.5) {
    warning("More than 50% of data is missing for this site/variable") # Warning if there exist many NAs
  }

  # Use cat instead of message to prevent double output
  cat("Correlation matrix for", variable,
      "from stream, precipitation, and soil solution (Site:", site,
      "; Years:", paste(range(year_range), collapse = "–"), ")\n") 

  round(cor(df, method = method), 2) #rounded correlation matrix to 2 decimal places
}

# function to summarise the correlation data in a table formate
summary_correlation_across_sites <- function(merged_df, variable, sites, year_range, method = "pearson") {
  result <- lapply(sites, function(site) {
    tryCatch({
      corr <- variable_correlation(merged_df, variable, site, year_range, method) # computing correlation
      data.frame(Site = site, 
                 Str_vs_Prec = corr[1, 2], 
                 Str_vs_Soil = corr[1, 3], 
                 Prec_vs_Soil = corr[2, 3],
                 stringsAsFactors = FALSE)
    }, error = function(e) { #if fail, return NA
      data.frame(Site = site, 
                 Str_vs_Prec = NA, 
                 Str_vs_Soil = NA, 
                 Prec_vs_Soil = NA,
                 stringsAsFactors = FALSE)
    })
  })

  do.call(rbind, result) #combining all the results into one dataframe
}

#a function to plot the correlation summary as a heatmap for visualisatio. 
plot_correlation_summary <- function(summary_df, variable) {
  summary_df_long <- summary_df %>%
    pivot_longer(cols = -Site, names_to = "Comparison", values_to = "Correlation") #reshape the dataframe for easier plotting

  ggplot(summary_df_long, aes(x = Comparison, y = Site, fill = Correlation)) +
    geom_tile() + # coloured tile heatmap
    geom_text(aes(label = round(Correlation, 2)), size = 3) + # add correlation coefficient over the heatmap for better visualisation
    scale_fill_gradient2(low = "darkblue", high = "maroon",  #colour coding
                         midpoint = 0, limit = c(-1, 1)) +
    theme_minimal() +
    labs(
      title = paste("Correlation Summary for", variable, "Across Sites"),
      x = "Comparison", y = "Site"
    ) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) # rotate x-axis labels for better readability
}
```

# Question 3

### 1. convert_to_weekly

#### Purpose:
Converts any water chemistry dataset into a weekly data by averaging repeated measurements within the week.

#### Arguments:

- df (data.frame): Input dataframes (e.g., df_stream_B, df_precipitation_B, df_soil_B). 

- date_col (character): Column name for date variable (default: "SDATE": no need to input)

- site_col (character): Column name for site code variable (default: "SITECODE": no need to input)

#### Returns:
A data frame sorted by site, year, and week, with averaged numeric variables for each weeks.

```{r}
# Example: (set the data into another dataframe for easier use in later functions)
df_stream_weekly <- convert_to_weekly(df_stream_B)
df_precipitation_weekly<- convert_to_weekly(df_precipitation_B)
df_soil_weekly<- convert_to_weekly(df_soil_B)
head(df_stream_weekly)
head(df_precipitation_weekly)
head(df_soil_weekly)
```

### 2. merge_datasets

#### Purpose:

Combines stream water, precipitation, and soil solution dataframes into a large  merged dataframe.

#### Arguments:

- stream (data.frame): Weekly stream dataset. (df_stream_weekly)

- precipitation (data.frame): Weekly precipitation dataset.(df_precipitation_weekly)

- soil(data.frame): Weeklysoil dataset.(df_soil_weekly)

(df_stream_weekly,  df_precipitation_weekly, df_soil_weeklyfrom last function's example)

#### Returns:
A data.frame merged by SITECODE, YEAR, and WEEK, with columns named like ALUMINIUM_str, ALUMINIUM_prec, ALUMINIUM_soil

```{r}
# Example: (set the data into another dataframe for easier use in later functions)
df_merged <- merge_datasets(df_stream_weekly, df_precipitation_weekly, df_soil_weekly)
head(df_merged)
```

### 3. remove_outliers

#### Purpose:

Removes outliers from the dataframe using the interquartile range method. Values outside $[Q1 - 1.5 \times \text{IQR},\ Q3 + 1.5 \times \text{IQR}]$ are replaced with NA.

#### Arguments:

- df_merged (data.frame): Merged dataset. (df_merged from last function, merge_datasets(), example)

#### Returns:
A data.frame with outlier values replaced by NA.

```{r}
# Example: (set the data into another dataframe for easier use in later functions)
df_merged_no_outliers <-remove_outliers(df_merged)
head(df_merged_no_outliers)
```

### 4. variable_correlation

#### Purpose:

Generate a correlation matrix for a given variable across the three water types for a given site and year range.

#### Arguments:

- df_merged_no_outliers (data.frame): Cleaned merged dataset. 

- variable (character): Name of the variable ("ALUMINIUM").

- site (character): Site code ("T02").

- year_range (numeric vector): Range of years to include (1992:1993). (data from 1992 to 2005)

- method (character): "pearson" (default) or "spearman". (no need to input)

#### Returns:
A 3×3 correlation matrix between the variable's values in _str, _prec, and _soil.

```{r}
#For example: Aluminuim at site T02 for 1992-1993 (do not set to dataframe)
variable_correlation(df_merged_no_outliers, "ALUMINIUM", "T02", 1992:1993)
```

### 5. summary_correlation_across_sites

#### Purpose:

Generates a summary table of pairwise correlations for a given variable across different data, for a given site and given year range.

#### Arguments:

- df_merged_no_outliers (data.frame): Cleaned merged dataset. 

- variable (character): Name of the variable ("ALUMINIUM").

- site (character): Site code ("T02").

- year_range (numeric vector): Range of years to include (1992:1993). (data from 1992 to 2005)

- method (character): "pearson" (default) or "spearman". (don't need to input)

#### Returns:
A data frame with correlations between water types.

```{r}
#For example: Aluminuim at site T02 for 1992-1993 (set the data into another dataframe for easier use in the last function)
summary_alum_T02_9293 <- summary_correlation_across_sites(df_merged_no_outliers, "ALUMINIUM", "T02", 1992:1993)
summary_alum_T02_9293
```

### 6. plot_correlation_summary

#### Purpose:
Generates a heatmap that provides visualisation for a given variable for a given year range.

#### Arguments:

- summary_df (summary_alum_T02_9293 from last function's example) (data.frame): Summary with site-wise correlations of an varianle between water types.

- variable (character): (Aluminium for example): Name of the variable (e.g., "ALUMINIUM").

#### Returns:
A data frame with site-wise correlations between water types for a given variablea nd year range.

```{r}
#For example: Aluminuim at site T02 for 1992-1993 
plot_correlation_summary(summary_alum_T02_9293, "ALUMINIUM")
```


# Question 4

## Hypotheses 1: 

```{r}
sites_1 <- c("T02", "T04", "T05", "T06", "T07", "T11") # sites we want to examine
summary_correlation_across_sites(df_merged_no_outliers, variable = "POTASSIUM", sites = sites_1, 2010:2015, method = "pearson") # input the dataframe without outliers, variable Potassium, listed sites, year range 2010-2015, and correlation method pearson
```

#### The abundance of Potassium (essential for fertile land) in soil solution is weakly positively correlated with stream water. This is supported by Str_vs_Soil Pearson correlations consistently falling within [0.15, 0.5] between 2010–2015 across sites T02, T07, T11, and T12, as shown in the summary table.


## Hypotheses 2: 

```{r}
sites_2 <- c("T02", "T04", "T05", "T07", "T12")
summary_correlation_across_sites(df_merged_no_outliers, variable = "NO3N", sites = sites_2, 1992:2015, method = "spearman")
```

#### TThere is no relationship of the abundance of Nitrate Oxygen (abundant in acid rain) in stream water and precipitation. The absolute values of the Str_vs_Prec Spearman correlations exceed 0.2 only twice during the full study period, as shown in the summary table across selected sites.

